---
title: "Miami Marlins Vs. Atlanta Braves 4/14/2021 Matchup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Installation of Singlearity

```{r}
install.packages("devtools")
devtools::install_github("singlearity-sports/singlearity-R")
```

## #Change R Environ in order to add API Key through R Studio or add the API key directly to your Renviron directly through Terminal on Mac.
```{r}
usethis::edit_r_environ()
```

## Library & API Load
```{r}
library(singlearity)
sing <- GetSinglearityClient()
```

# Make predictions for groups of batters vs groups of pitchers
```{r}
#List of batters
batter_list = c('Corey Dickerson', 'Starling Marte', 'Garrett Cooper', 'Brian Anderson', 'Adam Duvall', 'Jazz Chisholm', 'Miguel Rojas', 'Chad Wallach', 'Nick Neidert')

#List of pitchers
pitcher_list = c('Charlie Morton')

#initialize empty lists
candidate_batters <- list()
candidate_pitchers <- list()

for (batter in batter_list)
{
  candidate_batters <- append(candidate_batters, sing$GetPlayers(name=batter))
}

for (pitcher in pitcher_list)
{
  candidate_pitchers <- append(candidate_pitchers, sing$GetPlayers(name=pitcher))
}

venue <- sing$GetVenues(stadium.name = 'Truist Park')[[1]]
atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])

matchups <- list()
for (b in candidate_batters)
{
  for (p in candidate_pitchers)
  {
    matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = State$new()))
  }
}

results <- sing$GetPaSim(matchup = matchups)
results <- results[c('batter_name', 'pitcher_name', 'hr_exp', 'so_exp', 'ba_exp', 'ops_exp', 'woba_exp')]
results <- results[order(results$woba_exp, decreasing = TRUE), ]
print(results)
```

## This code generates heat maps of expected wOBA and K% values for every possible
## matchup from a list of batters and pitchers. In this case, it creates graphs that
## could be used by the Braves to select a relief pitcher, or the Marlins to select
## a pinch hitter.

```{r}
library(ggplot2)

batting_team = "Marlins"
pitching_team = "Braves"


candidate_batters = sing$GetPlayers(team.name=batting_team, active = TRUE, on.40 = TRUE)
candidate_pitchers = sing$GetPlayers(team.name=pitching_team, position = "P", active = TRUE, on.40 = TRUE)

venue <- sing$GetVenues(stadium.name = 'Truist Park')[[1]]
state <- State$new(pitch_number = 0, top = FALSE)
atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])


matchups <- list()
for (b in candidate_batters) 
{
  if (b$position == 'P')  #ignore pitchers batting
    next
  for (p in candidate_pitchers)
  {
    matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = state))
  }
}

results <- sing$GetPaSim(matchup = matchups)

# Generate wOBA heatmap
results = results[order(results$woba_exp, decreasing = TRUE), ]
ggplot(results, aes(pitcher_name, batter_name, fill = woba_exp)) + geom_tile() + scale_fill_distiller(palette = "Spectral")  +
  geom_text(aes(label = round(woba_exp, 3)), size=2) +theme(legend.position = "none", axis.text=element_text(size=5)) + labs(title="Predicted wOBA by Batter vs. Pitcher", subtitle="(Assumes 1st inning.  Pitcher pitch_count = 0.  No outs.  Bases empty.)") + theme(axis.text.x  = element_text(angle=90), plot.title = element_text(size=10, face="bold"), plot.subtitle= element_text(size=8))

# Generate strikeout heatmap
results = results[order(results$so_exp, decreasing = TRUE), ]
ggplot(results, aes(pitcher_name, batter_name, fill = so_exp)) + geom_tile() + scale_fill_distiller(palette = "Spectral")  +
  geom_text(aes(label = round(so_exp, 3)), size=2) +theme(legend.position = "none", axis.text=element_text(size=5)) + labs(title="Predicted K% by Batter vs. Pitcher", subtitle="(Assumes 1st inning.  Pitcher pitch_count = 0.  No outs.  Bases empty.)") + theme(axis.text.x  = element_text(angle=90), plot.title = element_text(size=10, face="bold"), plot.subtitle= element_text(size=8))


print(results)
atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])

matchups <- list()
for (b in candidate_batters)
{
  for (p in candidate_pitchers)
  {
    matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = State$new()))
  }
}

results <- sing$GetPaSim(matchup = matchups)
results <- results[c('batter_name', 'pitcher_name', 'hr_exp', 'so_exp', 'ba_exp', 'ops_exp', 'woba_exp')]
results <- results[order(results$woba_exp, decreasing = TRUE), ]
print(results)
```

#Shows each batter's expected wOBA as Charlie Morton's pitch count increases.

```{r}
#list of batters
batter_list = c('Corey Dickerson', 'Starling Marte', 'Garrett Cooper', 'Brian Anderson', 'Adam Duvall', 'Jazz Chisholm', 'Miguel Rojas', 'Chad Wallach', 'Nick Neidert')

#list of pitchers
pitcher_list = c('Charlie Morton')


#initialize empty lists
candidate_batters <- list()
candidate_pitchers <- list()

for (batter in batter_list)
{
  candidate_batters <- append(candidate_batters, sing$GetPlayers(name=batter))
}

for (pitcher in pitcher_list)
{
  candidate_pitchers <- append(candidate_pitchers, sing$GetPlayers(name=pitcher))
}


venue <- sing$GetVenues(stadium.name = 'Truist Park')[[1]]
atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])

j = 0
matchups <- list()
for (i in seq(0,105, by = 15)) {
  j = j+ 1
  for (b in candidate_batters) 
  {
    for (p in candidate_pitchers)
    {
      matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = State$new(pitch_number = i, inning = j, top = FALSE)))
    }
  }
}


results <- sing$GetPaSim(matchup = matchups)
results = results[order(results$woba_exp, decreasing = TRUE), ]
print(results)

ggplot(results, aes(p_pitch_no, woba_exp, color = batter_name)) + geom_smooth() + labs(title = "Batters vs. Charlie Morton wOBA by pitch count")
ggplot(results, aes(p_pitch_no, so_exp, color = batter_name)) + geom_smooth() + labs(title = "Batters vs. Charlie Morton K% by pitch count")
```

#Make predictions of batters vs. group of pitchers

```{r}
#list of batters
batter_list = c('Corey Dickerson', 'Starling Marte', 'Garrett Cooper', 'Brian Anderson', 'Adam Duvall', 'Jazz Chisholm', 'Miguel Rojas', 'Chad Wallach', 'Nick Neidert')

#list of pitchers
pitcher_list = c('Charlie Morton')

#initialize empty lists
candidate_batters <- list()
candidate_pitchers <- list()

for (batter in batter_list)
{
  candidate_batters <- append(candidate_batters, sing$GetPlayers(name=batter))
}

for (pitcher in pitcher_list)
{
  candidate_pitchers <- append(candidate_pitchers, sing$GetPlayers(name=pitcher))
}

venue <- sing$GetVenues(stadium.name = 'Truist Park')[[1]]
atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])

matchups <- list()
for (b in candidate_batters) 
{
  for (p in candidate_pitchers)
  {
    matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = State$new()))
  }
}

results <- sing$GetPaSim(matchup = matchups)
results = results[order(results$woba_exp, decreasing = TRUE), ]
print(results)
```
#situational Prediction

```{r}
pa_pred_simple <- function(batters = sing$GetPlayers(name="Miguel Rojas"),
                           pitchers = sing$GetPlayers(name="Charlie Morton"),
                           state =  State$new(), 
                           atmosphere = Atmosphere$new(venue = sing$GetVenues(stadium.name = 'Truist Park')[[1]], temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]]),
                           date = format(Sys.Date(), "%Y-%m-%d"),
                           predictiontype = 'ab_outcome'
                          ) {
  
  #initialize empty lists
  matchups <- list()
  
  for (b in batters) 
  {
    for (p in pitchers)
    {
      matchups <- append(matchups, Matchup$new(batter = b, pitcher = p, atmosphere = atmosphere, state = state, date = date))
    }
  }
  
  results <- sing$GetPaSim(matchup = matchups, model.name = predictiontype )
  results = results[order(results$woba_exp, decreasing = TRUE), ]
  return(results)
}

# Creates function to accept command-line arguments and run prediction function
# To run in the command line: 
# R -f pa_pred_simple.R --args [ARGUMENTS HERE]

if (sys.nframe() == 0) { #main function if run as stand-alone
  batters_list = c('Miguel Rojas')
  pitchers_list = c('Mike Clevinger')
  candidate_batters <- list()
  candidate_pitchers <- list()
  for (batter in batters_list)
  {
    candidate_batters <- append(candidate_batters, sing$GetPlayers(name=trimws(batter)))
  }
  
  for (pitcher in pitchers_list)
  {
    candidate_pitchers <- append(candidate_pitchers, sing$GetPlayers(name=trimws(pitcher)))
  }
  
  
  state <- State$new(inning = 7, 
                         top = TRUE,   #set top = FALSE for bottom of inning
                         on_1b = TRUE, 
                         on_2b = TRUE,
                         on_3b = TRUE, 
                         outs = 2, 
                         bat_score = 2,
                         fld_score = 3,
                         pitch_number = 83)
  venue <- sing$GetVenues(stadium.name = 'Truist Park')[[1]]
  atmosphere <- Atmosphere$new(venue = venue, temperature = 83, home_team = sing$GetTeams(name = 'Braves')[[1]])
   
 
  results = pa_pred_simple(batters = candidate_batters,
                              pitchers = candidate_pitchers,
                              state = state,
                              atmosphere = atmosphere)
  print(results)
  
}
```